Certificación Operativa Plataforma de Software trii

### 2025-01-25 output/texdoctec.2525581.tex
Compilación para entrega: 1.2525581.667ea6e: revision

Versión actual: 1.b606138 - Compilación para entrega: 1.5b6d694.3674428:
revision - Fri, 24 Jan 2025 23:07:07 +0000

@@

@@

1.6b2bb58 - build - Fri, 24 Jan 2025 18:01:03 -0500

>>>>

Versión actual: 1.2525581 - Compilación para entrega: 1.b606138.667ea6e:
revision - Fri, 24 Jan 2025 23:10:10 +0000

@@

1.2525581 - Compilación para entrega: 1.b606138.667ea6e: revision - Fri,
24 Jan 2025 23:10:10 +0000

@@
